Parallel training by Pipeline Execution In AIRCoP

### 2021-12-12 report/paper.tex
final version ready

In section \ref{evaluation}, we present a parallel training evaluation with different parallelism settings to illustrate the flexibility of our framework.

@@

  \includegraphics[scale=0.3]{NormalPipeline}

@@

  \includegraphics[scale=0.4]{stackedpipeline}

@@

During Collection Phase we need to collect the weight operations $E_w$, forward operations $E_f$ and backward operations $E_b$. For pipeline parallelism, we will add send/recv into $E_f$ and $E_b$ to maintain the data dependencies between modules. The corresponding variables of the operation is $xs^w$, $xs^f$, $xs^b$. We also need to calculate the lift variables $xs^l = Defined(E_f) \bigcap Used(E_b)$, the lifted variables $xs^l$ are the variables defined in the forward pass and used in the backward pass. Because we are generating different loops for forward passes and backward passes of micro-batches, we need to lift $xs^l$ into the outer scope and keep multiple versions of those variables for different micro-batches.\par

>>>>

In section \ref{evaluation}, we present a parallel training evaluation with different parallelism settings to illustrate the flexibility of our framework.\par
In section \ref{conclusion}, we summarize our progress and draw some conclusions.

@@

  \includegraphics[scale=0.4]{NormalPipeline}

@@

  \includegraphics[scale=0.45]{stackedpipeline}

@@

During Collection Phase we need to collect the weight operations $E_w$, forward operations $E_f$ and backward operations $E_b$. For pipeline parallelism, we will add send/recv into $E_f$ and $E_b$ to maintain the data dependencies between modules. The corresponding variables of the operation is $xs^w$, $xs^f$, $xs^b$. We also need to calculate the lift variables $$xs^l = Defined(E_f) \bigcap Used(E_b)$$, the lifted variables $xs^l$ are the variables defined in the forward pass and used in the backward pass. Because we are generating different loops for forward passes and backward passes of micro-batches, we need to lift $xs^l$ into the outer scope and keep multiple versions of those variables for different micro-batches.\par
